Measuring Individual Partisan Harm in Redistricting

### 2021-10-14 paper/paper.Rmd
discuss

We argue that understanding the redistricting process requires a feasible and reliable understanding of the counterfactual set of redistricting plans.
Our metrics offer a framework for understanding approximately individual harms, benefits, and net fairness.
Using counterfactual plans to understand this space allows us to properly calibrate understandings of the impact of redistricting plans on individual understanding.
Thus, we create measures which capture the possibility that no plans exist which favor one community [@duch:18].
Using this class of metrics which describe the individual affect via representation consequently allow us to better align legalistic interpretations of harm for standing with political science understandings.

@@

We should say something about the importance in developing further measures which utilize simulation approaches

@@

\begin{proof}
\end{proof}
```
# Computing Utility, Harm, and Fairness from Precinct-level Election Data {#app:formulas}

@@

Formulas here.

# Districting Measures in New Jersey {#app:nj}

>>>>

We argue that understanding the redistricting process requires a feasible and reliable understanding of the counterfactual set of redistricting plans.
Our metrics offer a framework for understanding approximately individual harms, benefits, and net fairness.
Using counterfactual plans to understand this space allows us to properly calibrate understandings of the impact of redistricting plans on individual understanding.
Thus, we create measures which capture the possibility that no plans exist which favor one community [@duch:18].
Using this class of metrics which describe the individual affect via representation consequently allow us to better align legalistic interpretations of harm for standing with political science understandings.
Standing itself is an individual endeavor. Individuals must show that they themselves have suffered injury directly, not just via the larger system they partake in [@1992lujan].

@@

This paper offers an attempt to bridge the quantitative gap between votes and representation. We break from existing redistricting literature and focus on the relationship between votes and representation by copartisans, rather than the relationship between votes and seats. This develops a new quantity of interest, partisan fairness, different from the standard of partisan symmetry for consideration.
Chiefly, this centers measurement strategies around how individual voters in a given geography would have likely faired under counterfactual plans, not how parties would have faired under symmetric elections.

This offers new purchase into the foundational questions of how to quantity the harms and benefits incurred to voters in district-based democracies--where the rules of defining districts are fixed, but the choice of how to how to draw the districts remains a policy question. This approach is flexible and we offer a baseline selection of clear and flexible, yet interesting, measures for improving the understanding of redistricting. Further work needs to be done to characterize how the potential rules of redistricting and other aspects, like the number or size of districts, impact these possibilities.

@@

\begin{proof}
\end{proof}
```
<!--
# Computing Utility, Harm, and Fairness from Precinct-level Election Data {#app:formulas}

@@

Formulas here.
-->
# Districting Measures in New Jersey {#app:nj}
